FraCaS: Temporal Analysis

### 2020-05-26 paper2020/paper.tex
Coq section

\paragraph{Coq}
If needed

>>>>

\paragraph{Coq}
 Coq is an interactive theorem prover (proof assistant). It is based on the
calculus of coinductive constructions (CiC), i.e.  a lambda calculus
with dependent types and coinduction (we do not use any coinduction in this paper).  Coq is a very powerful reasoning engine
that makes it fit for implementing natural language semantics in it but also, on a more practical side, for the the task of NLI, when the latter is formalized
as a theorem proving task. Coq supports, as already mentioned,
 dependent typing, but also subtyping, which are instrumental in
expressing NL semantics.
